sims

### 2024-10-01 sims/sims.Rmd
added code to simulate data and create figures

## create a function that can simulate hazrad functions between conditions ##

@@

```{r}
rt1_pid <- summary_pid(rt1) %>%
  mutate(example = "example 1")

rt1_group <- summary_group(rt1) %>% 
  mutate(example = "example 1")

rt2_pid <- summary_pid(rt2) %>% 
  mutate(example = "example 2")

rt2_group <- summary_group(rt2) %>% 
  mutate(example = "example 2")

rt3_pid <- summary_pid(rt3) %>% 
  mutate(example = "example 3")

rt3_group <- summary_group(rt3) %>% 
  mutate(example = "example 3")
```

@@

```{r}
rt4_pid <- summary_pid(rt4) %>%
  mutate(example = "example 4")

rt4_group <- summary_group(rt4) %>% 
  mutate(example = "example 4")

rt5_pid <- summary_pid(rt5) %>% 
  mutate(example = "example 5")

rt5_group <- summary_group(rt5) %>% 
  mutate(example = "example 5")

rt6_pid <- summary_pid(rt6) %>% 
  mutate(example = "example 6")

rt6_group <- summary_group(rt6) %>% 
  mutate(example = "example 6")
```

@@

```{r}
# p6.10 <- (p5.9 | p6.9) +
#   plot_layout(axes = 'collect')
# p6.10
```

@@

ggsave("sims/figures/haz_inset_facet.jpeg",
       width = 14, height = 10, dpi=800)
```

>>>>

## create a function that can simulate hazard functions between conditions ##

@@

```{r}
rt1_pid <- rt_pid(rt1) %>%
  mutate(example = "example 1")

rt1_group <- rt_group(rt1) %>% 
  mutate(example = "example 1")

rt2_pid <- rt_pid(rt2) %>% 
  mutate(example = "example 2")

rt2_group <- rt_group(rt2) %>% 
  mutate(example = "example 2")

rt3_pid <- rt_pid(rt3) %>% 
  mutate(example = "example 3")

rt3_group <- rt_group(rt3) %>% 
  mutate(example = "example 3")
```

@@

```{r}
rt4_pid <- rt_pid(rt4) %>%
  mutate(example = "example 4")

rt4_group <- rt_group(rt4) %>% 
  mutate(example = "example 4")

rt5_pid <- rt_pid(rt5) %>% 
  mutate(example = "example 5")

rt5_group <- rt_group(rt5) %>% 
  mutate(example = "example 5")

rt6_pid <- rt_pid(rt6) %>% 
  mutate(example = "example 6")

rt6_group <- rt_group(rt6) %>% 
  mutate(example = "example 6")
```

@@

```{r}
# p6.10 <- (p5.9 / p6.9) +
#   plot_layout(axes = 'collect',
#               guides = 'collect')
# p6.10
```

@@

ggsave("sims/figures/haz_inset_facet.jpeg",
       width = 14, height = 10, dpi=1000)
```

# section 9 #

## create a figure that illustrates hazard plus conditional accuracy ##

### create the hazard data ###

create hazard data

```{r}
## make it reproducible
set.seed(7)

## create the data
haz7 <- sim_haz(subj_n = 10, rep_n = 400, 
                hazard_cond2 = hazard_cond1*c(1, 1, 1, 1, 1, 0.5, 0.3, 0.2, 0.2, 0.2))
```

calculate summary hazard data

```{r}
haz7_pid <- haz_pid(haz7)
haz7_pid

haz7_group <- haz_group(haz7_pid)
haz7_group
```

plot hazard

```{r}
p9.1 <- haz_plot(haz7_pid, haz7_group) +
  labs(title = "hazard") +
  theme(legend.position = "none")
p9.1

## if you want to remove individual pid points for simplicity
# p9.1 <- p9.1 %>%  
#   remove_geom('point')
# p9.1
```

### convert to rt data ###

convert to rt data

```{r}
## make it reproducible
set.seed(7)

rt7 <- rt_dat(haz7)
head(rt7)
```

calculate summary rt data

```{r}
rt7_pid <- rt_pid(rt7)
rt7_pid

rt7_group <- rt_group(rt7)
rt7_group
```

simple plot rt

```{r}
# p9.2 <- rt_plot(rt7_pid, rt7_group)
# p9.2

p9.2 <- rt_plot_inset(rt7_pid, rt7_group)
p9.2
```

### inset rt within the hazard plot ###

```{r}
inset_hazrt <- tibble(
  x = 1,
  y = 0.9, 
  plot = list(p9.2)
)
```

and plot

```{r}
p9.3 <- p9.1 +
  geom_plot(data = inset_hazrt,
            vp.width = 1/3,
            aes(x, y, label = plot))
p9.3
```

### accuracy ###

create some data

```{r}
acc <- tibble(
  time = seq(1,10,1),
  cond1 = rep(1,length = 10),
  cond2 = c(0, 0, 0, 0, 0, 1, 1, 1, 1, 1)
) %>% 
  pivot_longer(-time,
               names_to = "condition",
               values_to = "accuracy") %>% 
  mutate(condition = factor(condition))
head(acc)
```

create group level summary data

```{r}
acc_group <- acc %>% 
  group_by(condition) %>% 
  summarise(group_accuracy = mean(accuracy, na.rm = TRUE),
            n=n(),
            group_sd=sd(accuracy, na.rm = TRUE),
            sem = (group_sd/sqrt(n)),
            .groups = "drop")
acc_group
```

line plot per bin

```{r}
p9.4 <-ggplot(acc, aes(x = time, y = accuracy,
                         colour = condition)) +
  geom_line(linewidth = 1) +
  geom_point(size=3) +
  scale_colour_brewer(palette = "Dark2") + 
  scale_x_continuous(breaks = 1:10) +
  scale_y_continuous(limits = c(0,1)) +
  xlab("timebin") +
  ylab("probability") +
  ggtitle("accuracy") 
p9.4
```

mean average plot

```{r}
p9.5 <- ggplot(acc, aes(x=condition, y = accuracy, 
                      fill = condition, colour = condition)) +
   geom_jitter(position=position_jitterdodge(dodge.width =1),
               alpha = 0.5) +
   geom_violin(alpha = 0.7) +
   geom_point(data = acc_group, 
             aes(y = group_accuracy), size = 2, position=pd2, colour = "black") +
   geom_errorbar(data = acc_group,
                aes(y = group_accuracy, ymin = group_accuracy-sem, ymax = group_accuracy+sem),
                width=.2, position=pd2, colour = "black") +
   geom_line(data = acc_group, 
            aes(y = group_accuracy, group=1),
            position=pd2,  colour = "black") +
   scale_fill_brewer(palette = "Dark2") +
   scale_colour_brewer(palette = "Dark2") +
   scale_y_continuous(limits = c(0, 1), breaks = seq(0,1,0.25)) +
   labs(y="",
        x="") +
   theme_bw() +
   theme(legend.position = "none",
         text = element_text(face = "bold"),
         panel.background = element_blank(),
         panel.grid.major = element_blank(),
         panel.grid.minor = element_blank())
p9.5
```

inset mean acc within the acc plot

```{r}
inset_acc <- tibble(
  x = 1,
  y = 0.9, 
  plot = list(p9.5)
)
```

and plot

```{r}
p9.6 <- p9.4 +
  geom_plot(data = inset_acc,
            vp.width = 1/3,
            aes(x, y, label = plot))
p9.6
```

## plot together ##

```{r}
p9.7 <- (p9.3 / p9.6) +
  plot_layout(guides = 'collect',
              axes = 'collect')
p9.7

## without inset
# ggsave("sims/figures/haz_acc.jpeg",
#        width = 8, height = 8, dpi=800)

## with inset
# ggsave("sims/figures/haz_acc_inset.jpeg",
#        width = 8, height = 8, dpi=800)
```

It doesn't make sense to create the inset with this data because the bins (1:10) are just to illustrate the point rather than being tied to actual RTs, like in a real study where bin 3 may represent 250-300ms say.

## create a figure that illustrates hazard and survivor functions ##

create the data

```{r}
data_hs <- tibble(
  timebin = seq(1,10,1),
  hazard = c(0, 0.02, 0.08, 0.19, 0.42, 0.52, 0.43, 0.41, 0.41, 0.39),
  survivor = c(1, 0.97, 0.91, 0.79, 0.61, 0.39, 0.22, 0.08, 0.04, 0.02)
) %>% 
  pivot_longer(-timebin,
               names_to = "dv",
               values_to = "probability") %>% 
  mutate(dv = factor(dv))
head(data_hs)
```

```{r}
p9.7 <-ggplot(data_hs, aes(x = timebin, y = probability,
                         colour = dv)) +
  geom_line(linewidth = 1) +
  geom_point(size=3) +
  scale_colour_brewer(palette = "Dark2") + 
  scale_x_continuous(breaks = 1:10) +
  scale_y_continuous(limits = c(0,1)) +
  ggtitle("hazard and survivor functions") 
p9.7

ggsave("sims/figures/haz_surv.jpeg",
       width = 7, height = 5, dpi=800)
```
